\documentclass[]{scrartcl}
\usepackage{src/cleancv}

\newcommand{\CVtype}{Curriculum Vit\ae}
\newcommand{\CVname}{Cara Kruse Hoppe}
\newcommand{\CVemail}{ckhoppe@gmail.com}
\newcommand{\CVdegrees}{MPH, MEd}
\newcommand{\CVphone}{$(702) \ 809-6469$}
\usepackage{enumitem}

\setlength{\WorkExperienceskip}{.6em}

\begin{document}
\begin{cleanCV}
  \SectionHead{Education}\vspace{-0.50em}
  
\WorkExperience
{Aug 2011}
{Master of Public Health}
{\\Drexel University}

\WorkExperience
{Dec 2007}
{Master of Education}
{\\Eastern University}

\WorkExperience
{Aug 2004}
{BA, Spanish Literature}
{\\University of Nevada}

\SectionHead{Certifications}
\vspace{-1.0em}


\WorkExperience
{2019}
{}
{Dyslexia Practitioner (WRS Level 1), Wilson Language Elementary \\
 Education (K-6), District of Columbia}

\WorkExperience
{2018}
{}{English as a Second Language (K-12), District of Columbia}
\vspace{-1.0em}
    
\SectionHead{Work Experience}
\vspace{0.50em}

\WorkExperience
{August - October 2020}
{English Language Specialist, Brazil\\}
{United States Department of State}

\JobDesc{}
{Plan and deliver 10 week online course for municipal teachers of English. Throughout the course teachers learned how to plan and implement Project Based Learning (PBL) for a language classroom. Lessons focused on virtual and in-person implementation. Additionally teacher leaders were trained to facilitate the course. Teachers earn a certification upon completion, awarded by the Municipal Secretariat of Education of Belo Horizonte, Brazil. The Secretariat of Education continues to use the course and the projects designed by teachers as part their English teacher professional development.}


\WorkExperience
{March - June 2020 \\ Volunteer}
{Falando com o Mundo Course Facilitator}
{\\Prefeitura de Belo Horizonte}

\JobDesc{}
{Plan and deliver 10 week online course for municipal teachers of English. The course aimed to increase teachers' facility with the English language while discussing current issues in Education. Teachers earned a certification upon completion, awarded by the Municipal Secretariat of Education.}

\WorkExperience{2019 - 2020}
{English Language Fellowship, Brazil}
{\\United States Department of State}

\JobDesc
{Municipal Secretariats of Education of Belo Horizonte \& Contagem: }
{Collaborate with the Secretariats of Education to create and facilitate training courses for municipal teachers of English. Provide instructional coaching to teachers based on the pedagogy presented during the course. Fellowship halted by U.S. Department of State in March 2020 due to COVID-19.}

\WorkExperience{August 2015 -\\ Present}
{Instructional Coach \& ELL Teacher}
{\\District of Columbia Public Schools}

\JobDesc
{Lafayette Elementary School: }
{Collect and analyze quantitative and qualitative instructional data in order to identify school, grade, teacher, and student level trends. Develop professional development plans based on data analysis. Provide strategic support aimed at increasing teacher effectiveness. Act as Academic Leadership Team member and ACCESS test chairperson.}

\WorkExperience{August 2014 -\\ June 2015}
{Curriculum Writer}
{\\CommonCore.Org}

\JobDesc
{ELA Curriculum, K-8: }
{Developed a scope and sequence of academic language for KIPP Foundation's K-8 curriculum. Collaborated with a team of grade-level curriculum writers to ensure selected terms were included in unit and daily lesson plans in a manner that reflected language acquisition pedagogy.}

\WorkExperience{June 2013 -\\ July 2015}
{Literacy Professional Learning Designer}
{\\District of Columbia Public Schools}

\JobDesc
{Office of Teaching and Learning: }
{Designed and implemented literacy professional development for over 1200 elementary teachers and 200 instructional coaches; session topics centered on implementation of Common Core State Standards and Language Use \& Acquisition. Partnered with school leadership teams and provided school-level support such as demo-lessons, on-site trainings, and data coaching to further support professional development.}



\WorkExperience{June 2012 -\\ December 2013}
{Adult ESOL \& Literacy - GED Program}
{\\Montgomery College, Part-Time Faculty}

\JobDesc
{Workforce development \& Continuing Education: }
{Developed curriculum based on students' needs and instructed adult English language learners using civics related topics. Created and administered formative assessments in order to focus instruction. Maintained confidential records required to ensure continued funding from federal and state agencies.}


\WorkExperience{Aug 2011 -\\ Aug 2012}
{Instructional Coach}
{\\District of Columbia Public Schools}

\JobDesc
{Marie Reed Bilingual School: }
{Collected quantitative and qualitative instructional data for English-only, Spanish Immersion, and ESL classes. Analyzed student data to determine instructional trends \& staff training needs. Developed \& facilitated professional training sessions. Provided strategic support aimed at increasing teacher effectiveness. Acted as a member of the  Student Support Team and the Academic Leadership Team. Supported staff in the development of a school-wide bilingual model.}

%\newpage

%\WorkExperience{2009-2011; 2006-2007}
%{English as a Second Language Instructor}
%{\\School District of Philadelphia}

%\JobDesc
%{Taggart Elementary School (2009-2011); (2005-2007): }
%{Conducted training for school staff as needed. Coordinated annual testing for English Language Learners. Co-taught with general education teachers to deliver ELL accommodations. Member of Distributive Leadership Team. Member of the Comprehensive Student Assistance Team ELL \& Literacy advisor.}

%\JobDesc
%{Pepper Middle School; Tilden Middle School (2006-2007): }
%{Traveled between locations to serve 5th-8th grade ELL populations. 
%Screened incoming students for English Language Proficiency.
%Created individual language development plans for all beginning ELL students.}

  
%\WorkExperience{2007-2009}
%{Spanish Instructor}
%{\\School District of Philadelphia - Charter School}

%\JobDesc
%{Global Leadership Academy Charter School: }
%{Developed K-8 Spanish as a Foreign Language curriculum for grades PK-8.
%Planned and implemented Spanish lessons for grades K-8.
%Organized cultural education trips for grades 6-8. 
%Awarded the Picasso Foundation's School Production Grant (Feb 2009).}

%\WorkExperience
%{Jan-Jul 2005}
%{Community Education Intern}
%{Planned Parenthood MarMonte}

%\JobDesc{}
%{Incorporated ages $18-24$ and University Housing into target demographic.
%Planned and presented sexual health presentations.
%Gathered and maintained data on outreach participants.}

%\WorkExperience
%{Jan-Jul 2005}
%{Outreach Intern}
%{Girls Scouts Sierra Nevada}

%\JobDesc{}
%{Collected, entered and managed data according to grant guidelines.
%Created and implemented program lessons for girls living in foster care.
%Organized and implemented Summer Day Camp for at risk girls.}

%\pagebreak

\SectionHead{Conferences \& Presentations}
\vspace{2.2em}

\Poster{2021 \\ (proposal accepted)}{
  ``Socratic Seminars in the Primary Classroom? Yes!'' (Facilitator)\\
  BrazTESOL}

%\Poster{DCPS}{District of Columbia Public Schools}

\Poster{2014}{
  Instructional Coaches Institute (Facilitator)\\
  District of Columbia Public Schools
}

\Poster{2013}{
  Using Multimedia to Accelerate Academic Language Proficiency (Facilitator)\\
  International TESOL Convention
}

\Poster{2012}{
  Common Core State Standards for ELLs (Facilitator)\\
  International TESOL Convention
}

\Poster{2012}{
  New Teacher Orientation Elementary ELA (Facilitator)\\
  District of Columbia Public Schools
}

\Poster{2012}{
  Common Core Reading Corps (Attendee)\\
  District of Columbia Public Schools
}

\Poster{2011}{
  Academic Language in the Content Areas:\\ Explicitly Teaching Tier 2 Vocabulary (Facilitator)\\
  District of Columbia Public Schools
}




%\Poster{2012}
%{Teaching English to Speakers of Other Languages\\
%(TESOL) Convention}

%\Poster{SDP}{School District Philadelphia}
%\Poster{TAGGERT}{Taggart Elementary School}

%\WorkExperienceX{}
%{International TESOL Convention}{}

%\Poster{March 2012}
%{Be Smart: Using Multimedia to\\ Accelerate Academic Language Proficiency }

%\WorkExperienceX{}{DCPS}{}

%\WorkExperienceX{}
%{DCPS\\Marie Reed Elementary School}{}

%\Poster{Jan 2012}
%{Struggling Readers:\\ Identifying Challenges \& Developing an Action Plan }

%\Poster{Nov 2011}
%{Facilitating Reading Conferences:\\ Using Reader's Responses to Inform Instructional Next-Steps}

%\Poster{Sept 2011}
%{Developing Readers \& Writers in the Primary Grades:\\ Connecting Theory to Practice}

%\WorkExperienceX{}
%{SDP}{}

%\Poster{Nov 2010}
%{Co-teaching: Models and Methods}

%\Poster{Sept 2010}
%{Lesson Scaffolding for Low Performing Students}

%\Poster{Nov 2009}
%{Academic Language Acquisition in the Content Areas}

\end{cleanCV}
\end{document}


