\documentclass[]{scrartcl}
\usepackage{src/cleancv}

\newcommand{\CVtype}{Student Resume}
\newcommand{\CVname}{Jackson Hoppe}
\newcommand{\CVemail}{XXXXXXX@gmail.com}
\newcommand{\CVdegrees}{Born: June 2008}
\newcommand{\CVphone}{$(775) \ 287-4033$}
\usepackage{enumitem}

\setlength{\WorkExperienceskip}{.6em}

\begin{document}
\begin{cleanCV}

  \SectionHead{Education}
  \vspace{-0.50em}

\WorkExperience
{2022 - current}
{Richard Montgomery High School (Freshman)\\}
{Regular volunteer at local elementary schools to help teachers with administrative tasks. Working towards the Student Service Learning (SSL) recognition on graduation. }
\vspace{-0.5em}

\WorkExperience
{2020 - 2022}
{Julius West Middle School}{}
\vspace{-0.5em}


\SectionHead{Work Experience}
\vspace{0.50em}

\WorkExperience{2018 -\\ Present}
{Outdoor yard and construction work}
{}
\JobDesc{\\Montgomery County - }
        {Maintained and improved front and back yards by performing tasks such as weeding, surfacing, and assisting with various other yard duties as required. Assisted with painting, digging, and installation of fencing as instructed by superiors. Kept accurate and updated task reports and time sheets for regular submission to the supervisor.}

\WorkExperience
{August - November 2021}
{Busboy and dishwasher}
{}
\JobDesc{\\Tempe City Tacos, AZ - }
        {
          Experience in food and beverage industry with back-of-house experience at high-volume restaurant.
          Cleaned, sanitized, and restocked dishes, glassware, and utensils, using proper levels of detergent and sanitizer.
          Swept and mopped floors, and cleared tables as needed.
}

\SectionHead{Work Statement}
\vspace{-1.50em}

\WorkExperience
{}
{}
{}
\JobDesc{}
        {As a highly driven and enthusiastic young professional, I am fully committed to putting in the necessary effort and time to demonstrate my aptitude and potential for success. I am eager to take on new challenges and learn the skills required to excel in this role. With a strong work ethic and a passion for growth, I am confident that I can make a valuable contribution to your organization. }

\pagebreak

\end{cleanCV}
\end{document}


