\documentclass[]{scrartcl}
\usepackage{src/cleancv}

%\newcommand{\CVtype}{Curriculum Vit\ae}
%\newcommand{\CVdegrees}{PhD Physics}

\newcommand{\CVtype}{\vspace{-1em}}
\newcommand{\CVdegrees}{\vspace{-1em}}
\newcommand{\CVname}{Travis Aaron Hoppe, P\MakeLowercase{h}D}
\newcommand{\CVemail}{travis.hoppe@gmail.com}
\newcommand{\CVphone}{$(775) \ 287\hbox{-}4033$}



\begin{document}
\begin{cleanCV}

  \vspace{2em}
  \begin{raggedright}
    \textbf{Office of Portfolio Analysis (OPA)} \newline
    \hangindent=0.7cm \indent Division of Program Coordination, Planning,
    and {Strategic Initiatives} (DPCPSI),
    National Institutes of Health (NIH)
  \end{raggedright}
  
  \vspace{2em}

  To whom it may concern,

  \vspace{1em}
  \setlength{\parskip}{1em}
  
  I am applying for the position advertised in an internal email bulletin.
  The position is looking for an individual to analyze the NIH investment in science using modern data analysis tools.
  I am uniquely qualified for this position and I am willing to start immediately.

  In addition to the standard skillset and research portfolio required for a computational biophysicist, I have a track record of producing novel and interesting data-driven projects.
  Closely related to the mission statement of the OPA, I've already personally studied the effects of authorship in the health-related sciences.\footnote{
    \href{http://thoppe.github.io/Presentation_Rise_of_the_Coauthor}{Rise of the Coauthor}
  }
  I recently wrote a program to fool the popular website Reddit for months at a time by text-mining previous submissions to build a model of interesting posts.\footnote{
    Buzzfeed News: \href{http://www.buzzfeed.com/hamzashaban/today-ai-learned}{Meet The Man Who Gamed Reddit With A Bot}
  }
  This `bot' learned human-behavior and mined Wikipedia for new content.
  I've analyzed programming code as natural language and found surprising results.\footnote{
    Github: \href{http://thoppe.github.io/code-linguistics/HnC_presentation.html}{Code Linguistics}
  }
  I've even written a deep-learning model for natural language concepts to determine conceptual paths between words.\footnote{
    Github: \href{https://github.com/thoppe/transorthogonal-linguistics}{Transorthogonal Linguistics}, Heroku: \href{http://transorthogonal-linguistics.herokuapp.com/TOL/boy/man}{demo}
  }
  Please follow the hyperlinks in this cover letter.
  Play around with the presentations and programs and feel free to ask me any questions on how these skills could be directly applied to the mission of the OPA.

  I recognize that strong interpersonal skills are required to convey any idea, from a standard briefing to a scientific breakthrough.
  This is why I'm a leader in the local data-science community.
  I've presented over a dozen times at local Universities and meetups in the DC area.
  I am the organizer of a 850 member meetup called Hack and Tell,\footnote{
    Meetup.com: \href{http://www.meetup.com/DC-Hack-and-Tell/}{Hack and Tell}
  } an organization designed to showcase some of the new and novel projects created by local enthusiasts.

  As this is my final year as a postdoctoral fellow, I'd like to explore new avenues of employment outside of the direct tenure-track academic path.
  I'm looking forward to this detail to make contacts and hopefully advance the mission of scientific reporting and assessment within our community.

  Sincerely,\newline
  \emph{Travis Hoppe}
  
\end{cleanCV}
\end{document}


