\documentclass[]{scrartcl}
\usepackage{src/cleancv}

\newcommand{\CVtype}{Curriculum Vit\ae}
\newcommand{\CVname}{Cara Kruse Hoppe}
\newcommand{\CVemail}{ckhoppe@gmail.com}
\newcommand{\CVdegrees}{MPH, MEd}
\newcommand{\CVphone}{$(702) \ 809-6469$}

\setlength{\WorkExperienceskip}{.6em}

\begin{document}
\begin{cleanCV}
\SectionHead{Education}
\WorkExperience
{Aug 2011}
{Master of Public Health}
{Drexel University}

\WorkExperience
{Dec 2007}
{Master of Education}
{Eastern University}

\WorkExperience
{Aug 2004}
{BA, Spanish Literature}
{University of Nevada}

\SectionHead{Experience}

\WorkExperience{June 2014 -\\ Present}
{Curriculum Writer}
{CommonCore.Org}

\JobDesc
{ELA Curriculum, K-8: }
{Develop a scope and sequence of academic language for KIPP Foundation's K-8 curriculum. Collaborate with a team of grade-level curriculum writers to ensure selected terms are included in unit and daily lesson plans in a manner that reflects language acquisition pedagogy.}

\WorkExperience{June 2013 -\\ Present}
{Literacy Professional Learning Designer}
{District of Columbia Public Schools}

\JobDesc
{Office of Teaching and Learning: }
{Design and implement literacy professional development for over 1200 elementary teachers and 200 instructional coaches; session topics centered on implementation of Common Core State Standards and Language Use \& Acquisition. Partner with school leadership teams and provide school-level support such as demo-lessons, on-site trainings, and data coaching to further support professional development.}

\WorkExperience{June 2012 -\\ Present}
{Adult ESOL \& Literacy - GED Program}
{Montgomery College, Part-Time Faculty}

\JobDesc
{Workforce development \& Continuing Education: }
{Develop curriculum based on students' needs and instruct adult English language learners using Civics related topics. Create and administer formative assessments in order to focus instruction. Maintain confidential records required to ensure continued funding from federal and state agencies.}

\WorkExperience{Aug 2011 -\\ Aug 2012}
{Instructional Coach}
{District of Columbia Public Schools}

\JobDesc
{Marie Reed Elementary School: }
{Collected quantitative and qualitative instructional data. Analyzed student data to determine instructional trends \& staff training needs. Developed \& facilitated professional training sessions. Provided strategic support aimed at increasing teacher effectiveness. Acted as a member of the  Student Support Team and the Academic Leadership Team}

\newpage

\WorkExperience{2009-2011; 2006-2007}
{English as a Second Language Instructor}
{School District Philadelphia}

\JobDesc
{Taggart Elementary School (2009-2011);(2005-2007): }
{Conducted training for school staff as needed. Coordinated annual testing for English Language Learners. Co-taught with general education teachers to deliver ELL accommodations. Member of Distributive Leadership Team. Member of the Comprehensive Student Assistance Team ELL \& Literacy advisor.}

\JobDesc
{Pepper Middle School; Tilden Middle School (2006-2007): }
{Traveled between locations to serve 5th-8th grade ELL populations. 
Screened incoming students for English Language Proficiency.
Created individual language development plans for all beginning ELL students.}

  
\WorkExperience{2007-2009}
{Spanish Instructor}
{School District Philadelphia - Charter School}

\JobDesc
{Global Leadership Academy Charter School: }
{Developed K-8 curriculum for grade PK-8.
Planned and implemented Spanish lessons for grades K-8.
Established travel abroad program for grade 8.
Organized cultural education trips for grades 6-8. 
Awarded the Picasso Foundation's School Production Grant (Feb 2009)}

%\WorkExperience
%{Jan-Jul 2005}
%{Community Education Intern}
%{Planned Parenthood MarMonte}

%\JobDesc{}
%{Incorporated ages $18-24$ and University Housing into target demographic.
%Planned and presented sexual health presentations.
%Gathered and maintained data on outreach participants.}

%\WorkExperience
%{Jan-Jul 2005}
%{Outreach Intern}
%{Girls Scouts Sierra Nevada}

%\JobDesc{}
%{Collected, entered and managed data according to grant guidelines.
%Created and implemented program lessons for girls living in foster care.
%Organized and implemented Summer Day Camp for at risk girls.}

%\pagebreak

\SectionHead{Conferences \& Presentations}
\vspace{2.2em}


\newcommand{\DCPS}{District of Columbia Public Schools}

\newcommand{\DCOR}
{District of Columbia Public Schools\\
Office Professional Development: Coaches Institute}

\newcommand{\TSOL}
{Teaching English to Speakers of Other Languages\\
(TESOL) Convention 2012}

\newcommand{\SDP}{School District Philadelphia}
\newcommand{\TAGGERT}{Taggart Elementary School}

\WorkExperienceX{}
{Teaching English to Speakers of Other Languages (TSOL)}{}

\Poster{March 2013}
{Be Smart: Using Multimedia and\\Common Core State Standards for ELLs}

\Poster{March 2012}
{Be Smart: Using Multimedia to\\ Accelerate Academic Language Proficiency }

%\WorkExperienceX{}{\DCPS}{}

%\Poster{August 2012}
%{New Teacher Orientation - Elementry \& Special Education ELA }

%\Poster{June 2012}
%{Common Core Reading Corps }

%\WorkExperienceX{}
%{\DCPS\\Marie Reed Elementary School}{}

%\Poster{Jan 2012}
%{Struggling Readers:\\ Identifying Challenges \& Developing an Action Plan }

%\Poster{Nov 2011}
%{Facilitating Reading Conferences:\\ Using Reader's Responses to Inform Instructional Next-Steps}

%\Poster{Oct 2011}
%{Academic Language Acquisition in the Content Areas:\\ Explicitly Teaching Tier 2 Words}

%\Poster{Sept 2011}
%{Developing Readers \& Writers in the Primary Grades:\\ Connecting Theory to Practice}

\WorkExperienceX{}
{\SDP}{}

\Poster{Nov 2010}
{Co-teaching: Models and Methods}

\Poster{Sept 2010}
{Lesson Scaffolding for Low Performing Students}

\Poster{Nov 2009}
{Academic Language Acquisition in the Content Areas}

\end{cleanCV}
\end{document}


