\documentclass[]{scrartcl}
\usepackage{src/cleancv}

%\newcommand{\CVtype}{Curriculum Vit\ae}
%\newcommand{\CVdegrees}{PhD Physics}

\newcommand{\CVtype}{\vspace{-1em}}
\newcommand{\CVdegrees}{\vspace{-1em}}
\newcommand{\CVname}{Travis Aaron Hoppe, P\MakeLowercase{h}D}
\newcommand{\CVemail}{travis.hoppe@gmail.com}
\newcommand{\CVphone}{$(775) \ 287\hbox{-}4033$}

\titleformat{\section}[block]{\noindent\bfseries}{}{0em}{} 
\titleformat{\subsection}[block]{\noindent\itshape}{}{0em}{} 

\titlespacing*{\section}
{0pt}{0ex}{0ex}
\titlespacing*{\subsection}
{0pt}{1ex}{1ex}

\begin{document}
\begin{cleanCV}

\vspace{-1em}

\SectionHead{Highlights}

\Highlight
{Established scientist}
{Eleven publications (six first-author) across multiple disciplines in Nature, PLoS One, Physical Review and more.}

\Highlight
{Project leader and team coordinator}
{Served as the principal investigator for several projects managing small teams for highly technical tasks.}

\Highlight
{Programming polyglot and dedicated analyst}
{Highly proficient in the full scientific python/C++ stack, database backends, and data visualization. 
Proponent for scientific standards and reproducibility.}

\Highlight
{Professional outreach}
{Active presenter and organizer in both the data community (Data Wranglers and Hack \& Tell) and scientific enterprise (Biophysical society, American Physical Society, and more). Firm believer in STEM outreach to public schools from professionals.}

\SectionHead{Education}

\WorkExperience
{2011}
{Doctor of Philosophy, Physics}
{Drexel University, awarded multiple scientific grants and winner of the top teaching fellow for the University.}

\WorkExperience
{2005}
{Bachelor of Science Physics, Bachelor of Science Mathematics}
{University of Nevada, served on student-body Senate where state-level legislation was proposed to standardize and publish professor evaluations.}


\SectionHead{Experience}

\WorkExperience
{2014-current}
{Postdoctoral Fellowship, Intramural Research Program}
{
Fellowship at the National Institutes of Health (NIH) in the Theoretical Biophysics laboratory serving under Robert Best.
Established and published key results with our team concerning bioinformatics and internal friction for the protein folding problem.
}

\WorkExperience
{2011-2014}
{Research Associate}
{
Worked in the Physical Biochemistry laboratory at the NIH with Allen Minton to develop multi-scale theoretical and computational models to study protein folding, structure, and protein-protein interactions.
Worked in direct collaboration with experimentalists to test and validate models.
Designed and managed large-scale parallel programming projects (3000+ cores).
}

\WorkExperience
{2005-2011}
{Teaching Assistant}
{%
  Organized, taught, and ran over 22 undergraduate courses at Drexel university.
  Developed lesson plans and curricula.
  Restructured the entire computational component for physics majors by transitioning from FORTRAN to Python.
}

\SectionHead{Skills}

\SkillSet{Programming}{
  \Skill{Core Languages}{Python, C++, C},
  \Skill{Web Design} {HTML5, JavaScript, AWS},
  \Skill{Visualization} {d3, TikZ},
  \Skill{Database}{SQLite, HDF5}, 
  \Skill{Typesetting}{\LaTeX}
  \Skill{Version Control}{git, mercurial}.
}

\SkillSet{Data Science}{
  \Skill{Machine Learning}{Random Forests, Recurrent Neural Networks}, 
  \Skill{Graph Theory}{Network Flow Analysis, Isomorphism detection, Topology},
  \Skill{Dimensionality Reduction}{Spectral Clustering, Principal Component Analysis},
  \Skill{Natural Language Processing}{Semantic Analysis, Context Free Grammars},
  \Skill{Data Wrangling}{web spiders, data acquisition},
  \Skill{Statistics}{Bayesian, Maximum Likelihood},
  \Skill{Game Theory}{Nash Equilibrium}.
}

\end{cleanCV}
\end{document}


