\documentclass[]{scrartcl}
\usepackage{src/cleancv}

%\newcommand{\CVtype}{Curriculum Vit\ae}
%\newcommand{\CVdegrees}{PhD Physics}

\newcommand{\CVtype}{\vspace{-1em}}
\newcommand{\CVdegrees}{\vspace{-1em}}
\newcommand{\CVname}{Travis Aaron Hoppe, P\MakeLowercase{h}D}
\newcommand{\CVemail}{travis.hoppe@gmail.com}
\newcommand{\CVphone}{$(775) \ 287\hbox{-}4033$}



\begin{document}
\begin{cleanCV}

  \vspace{2em}
  \begin{raggedright}
    \textbf{Head of AI} \newline
    \hangindent=0.7cm \indent
    Chan Zuckerberg Initiative
  \end{raggedright}
  
  \vspace{2em}
  
  Dear Committee Members,

  \vspace{1em}
  \setlength{\parskip}{1em}


CZI’s ambition to harness artificial intelligence in service of curing, preventing, and managing disease resonates deeply with my own conviction that AI—carefully guided—can become one of humanity’s most powerful public goods. During the past decade I have led national-scale AI and data-science programs at the White House, the Centers for Disease Control and Prevention, and the National Institutes of Health, always at the nexus of technology, bioscience, and public health. Those experiences have taught me that when AI is paired with rigorous biological insight and clear guiding principles, it can deliver abundance: accelerating discovery, widening access, and addressing urgent human needs.

As Assistant Director for AI R\&D in the White House Office of Science and Technology Policy, I set the federal vision for initiatives such as the National AI Research Resource, stewarded multi-agency investments, and convened cross-sector coalitions—from Tribal governments to Fortune 500 biotech firms—to translate research breakthroughs into measurable health impact.
At CDC, where I now serve as Acting Chief AI Officer, I launched the first government‑wide generative‑AI pilots, modernized national health‑data infrastructure, and shipped privacy‑preserving analytics that scaled to millions of sensitive records—all while mentoring multidisciplinary teams of machine‑learning engineers, immunologists, statisticians, and policy experts.

These roles mirror the responsibilities outlined for CZI’s Head of AI: defining bold, goals-based science, shepherding high‑risk/high‑reward programs, and forging partnerships that dissolve the barriers between academia, philanthropy, and industry. My publication record—ranging from fundamental protein‑folding physics to The Pile, one of the first open datasets large‑language‑model training—shows both depth in the biosciences and breadth across AI methodology. Equally important, I have demonstrated that strategic, values‑driven investment can turn cutting‑edge research into equitable, real‑world benefit.

I am proud of the progress I enable every day for public‑health colleagues at CDC, yet I feel called to an even broader canvas—one that spans the full spectrum of biomedical research and leverages CZI’s unparalleled philanthropic resources. I would be honored to lead CZI’s AI efforts and help enact a bold AI strategy that hastens the end of disease and for all people fairly.

  Sincerely,\newline
  \emph{Travis Hoppe}, PhD
  
\end{cleanCV}
\end{document}


